Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-24 appendix.tex
tex

>>>>

\section{More Details Explained}

In this section, we provide more details on the reasons of our design,
additional details of our implementation, as well as more discussions
on questions that are unsuitable for the main part of manuscript.

\begin{enumerate}[noitemsep]
	\item Only aap in ICS?
	\item Why not aa~p~ in ICS?
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
	\item Another example for the GA pseudo-hardness function family?
	\item Why not ResNet-50?
\end{enumerate}

\section{Visualizations}

Visualize robustness through the image retrieval task.

### 2021-10-24 robdml.tex
tex

This section is organized in logical order where a group of experiments
or ablation study
provides clues for the next group of experiment.
%
Hence, the comparison to the state-of-the-art works are put at the last
subsection.

>>>>

In this section, we first carry out parameter search for the components of the
proposed method, in order to illustrate their effectiveness.
%
The comparison with the state-of-the-art DML defense methods will be presented in the end.
